Exploring Income Inequality Dynamics in Canada: A Geospatial and Temporal Analysis

### 2024-04-03 paper/paper.qmd
upload the pdf

-   $\beta_{2}$ represents the coefficient for the variable $Province_{j}$, indicating the effect of province on income inequality. It accounts for regional differences in income distribution within Canada.

@@

-   $Y_{i}$ represents the income range for a particular combination of year ($Year_{i}$) and geographical location ($Province_{j}$).

@@

- $\beta_{2}$ is the coefficient associated with the "Geographical Location" variable (\(Province_{j}\)), representing the average difference in income range between different provinces, holding the year constant.

@@

The first model (Equation 1) aims to capture the relationship between the response variable, $y_i$, representing the highest-to-lowest average income ratio of average after-tax income to the lowest decile of average after-tax income of Canada in the $i^{th}$ year and province $j$, and the predictor variables, $\text{Year}_i$ and $\text{Geographical Location}_i$.

@@

Model (\ref{eq-model2}) is formulated to explore the relationship between the income range ($Y_{ij}$) and the predictor variables, Year ($Year_{i}$), and Geographical Location ($Province_{j}$).

$Y_{ij}$ represents the income range for a specific combination of year ($Year_{i}$) and geographical location ($Province_{i}$). This formulation allows us to examine how income ranges vary across different years and provinces.

>>>>

-   $\beta_{2}$ represents the coefficient for the variable $Province_{i}$, indicating the effect of province on income inequality. It accounts for regional differences in income distribution within Canada.

@@

-   $Y_{i}$ represents the income range for a particular combination of year ($Year_{i}$) and geographical location ($Province_{i}$).

@@

- $\beta_{2}$ is the coefficient associated with the "Geographical Location" variable (\(Province_{i}\)), representing the average difference in income range between different provinces, holding the year constant.

@@

The first model (Equation 1) aims to capture the relationship between the response variable, $y_i$, representing the highest-to-lowest average income ratio of average after-tax income to the lowest decile of average after-tax income of Canada in the $i^{th}$ year and province $i$, and the predictor variables, $\text{Year}_i$ and $\text{Geographical Location}_i$.

@@

Model (\ref{eq-model2}) is formulated to explore the relationship between the income range ($Y_{i}$) and the predictor variables, Year ($Year_{i}$), and Geographical Location ($Province_{i}$).

$Y_{i}$ represents the income range for a specific combination of year ($Year_{i}$) and geographical location ($Province_{i}$). This formulation allows us to examine how income ranges vary across different years and provinces.
